
An Introduction to Statistical Learning with Applications in R: Chapter III'
============================================================

** Q:** Describe the null hypotheses to which the p-values given in Table 3.4
correspond. Explain what conclusions you can draw based on these
p-values. Your explanation should be phrased in terms of sales, TV,
radio, and newspaper, rather than in terms of the coefficients of the
linear model.

** Answer: **
Table 3.4 shows the regression statistics from predicting y = sales using TV, Radio, and Newspaper.


```{r}
data <- data.frame(coef = c('$\\hat{\\beta_{0}}$ = 2.93', '$\\hat{\\beta_{1}}$ = 0.46', '$\\hat{\\beta_{2}}$ = 0.189', '$\\hat{\\beta_{3}}$ = -0.001'), 
std_err = c(0.3119, 0.0014, 0.0086, 0.0059), t_stat = c( 9.42, 32.81, 21.81, -0.18),
p_value = c('< 0.0001', '< 0.0001', '< 0.0001', '0.8599'), stringsAsFactors = FALSE)

colnames(data) <- c("coefficient", "std.error", "t-statistic", "p-value")
rownames(data) <- c("Intercept", "`TV`", "`Radio`", "`Newspaper`")

library(kableExtra)
kable(data, row.names = TRUE) %>% kable_styling(bootstrap_options = "bordered", full_width = FALSE)
```

**(a) Intercept**

The corresponding test (with null and alternative hypotheses):

This summation expression is in display form.

$\\sum_{i=1}^n X_i$



```{r}
